Recurrence spike spectra

### 2022-07-14 Manuscript/inter_spike_manuscript.tex
add frequency part

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
%
% Insert the name of "your journal" with
\journalname{Nonlinear Dynamics}
%
\begin{document}

@@

\author{K. Hauke Kraemer \and
		Frank Hellmann \and
        J\"urgen Kurths \and 
        Norbert Marwan
}

@@

lalalalalala
lalalal \\

lalala\\
\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra_lasso_standard_20s}
 \caption{THIS WILL BE A HIGH-RES FIGURE SOON AND A CAPTION WILL BE ADDED  
}
\label{fig_power_spectra_frequency}
\end{figure}

@@

% Non-BibTeX users please use
\bibliographystyle{spbasic} 
\bibliography{inter_spike_bib}

>>>>

%
\smartqed  % flush right qed marks, e.g. at end of proof
%
\usepackage{graphicx}
%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
\setlength{\marginparwidth}{2cm}
\usepackage{changes}
\usepackage{bbm}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{statmath}
\usepackage[numbers]{natbib}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{mathtools}
\usepackage{siunitx}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
%
% please place your own definitions here and don't use \def but
\newcommand{\mytilde}{\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}}
%
% Insert the name of "your journal" with
\journalname{Nonlinear Dynamics}
%
\begin{document}

@@

\author{K. Hauke Kraemer \and
		Frank Hellmann \and
		Mehrnaz Anvari \and
        J\"urgen Kurths \and 
        Norbert Marwan
}

@@

Power grids are a large synchronized complex network that modern societies are depend on the stable functionality of them. To maintain the stability of a power grid, the balance between the energy consumption and energy production should be provided. In an AC-power grid, the grid frequency is an observable variable that reflects how well this balance is satisfied. Thereby, the grid frequency and, indeed its variations over the nominal frequency (which is $50$ \si{Hz} in Europe and many parts of the world, or $60$ \si{Hz} in the Americas, Southern Japan and some other
regions) is continuously recorded and monitored by grid operators. For instance, in the case that there is more (less) demand than supply, the grid frequency decreases (increases) form nominal frequency \cite{}.
\\

The frequency variations can include other information, such as the functionality of control systems \cite{}, the effect of fluctuations in
renewable energies (REs) and demands on the grid \cite{} and, moreover, the effect of regular dispatches due to the trading market \cite{}. The latter induce periodic frequency jumps. The frequency trajectory for the Great Britain (GB) grid Continental Europe (CE) grid shown in Fig.~\ref{} demonstrates clear jumps every hour {\color{red} (maybe we should add this figure and one from auto-correlation or $\tau$-RP)}. Moreover, autocorrelation/$\tau$-RP shows the regular peaks every $30$ \si{min} and one hour (see Fig.~\ref{}). These peaks are caused by a mismatch of power
supply and demand \cite{} during dispatches. In most electricity grids the
operation of dispatchable power plants is scheduled in one hour blocks, where additional (shorter) $30$ and $15$ \si{min} intervals
might exist. Hence\\

\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{./figures/fig_power_grid_spectra_lasso_standard_20s}
 \caption{THIS WILL BE A HIGH-RES FIGURE SOON AND A CAPTION WILL BE ADDED  
}
\label{fig_power_spectra_frequency}
\end{figure}

@@

% Non-BibTeX users please use
\bibliographystyle{spbasic} 
\bibliography{in\\
	pike_bib}
